Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-09-28 src/docs_28-09-22-toronto/28-09-22-toronto.Rmd
Spotted typos during talk

* The Global AIDS strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
  1. Population-level HIV incidence
  2. Individual-level sexual risk behaviour
* Takes into account the two most proximal drivers of sexual transmission

@@

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
$\implies$ Estimates of risk group proportions $\rho_{itak}$ by district, year and age group
\end{tcolorbox}
\end{center}

>>>>

* The Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based upon
  1. Population-level HIV incidence
  2. Individual-level sexual risk behaviour
* Takes into account the two most proximal drivers of sexual transmission

@@

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
$\implies$ Estimates of risk group proportions $p_{itak}$ by district, year and age group
\end{tcolorbox}
\end{center}
